### 2015-09-18 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: began adding code for specific hose stream report plots

\headerC{
{
\flushright{
Joseph Willi \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\

@@

Test 33 involved flowing water using a monitor equipped with a combination nozzle from Room C to the ceiling of Room B in the East Structure (Fig.~\ref{fig:test_33_pic}). A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

@@

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle. The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated for the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

\subsection{Handline Experiments}
\label{subsec:handline_procedure}
Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water. One test series, Test 34, occurred in the East Structure, and the two other series, Tests 18 and 19, occurred in the West Structure.

Test 34 involved flowing water using a 1.75" handline equipped with a combination nozzle located inside Room C. A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}. Next, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. This process were repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 34]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 34}
\label{fig:test_34_pic}
\end{figure}
\FloatBarrier

% Where was the handline aimed? Add flow chart? %
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.

\begin{figure}[!ht]
\includegraphics[width=4.25in]{../Pictures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\clearpage

@@

% \begin{figure}[!ht]
% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
% \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
% \label{fig:Test_16_BDP_A10_Avg_All}
% \end{figure}

>>>>

\headerC{
{
\flushright{
Joseph M. Willi \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\

@@

Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}). A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

@@

% Add flow chart? %
Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle. The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall. Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

\subsection{Handline Experiments}
\label{subsec:handline_procedure}
Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water. One test series, Test 34, occurred in the East Structure, and the other two series, Tests 18 and 19, occurred in the West Structure.

During Test 34, water was flowed from a 1.75" handline equipped with a combination nozzle located inside Room C. A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}. The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}. Next, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. This process were repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
\\~\\
\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 34]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 34}
\label{fig:test_34_pic}
\end{figure}

% Where was the handline aimed? Add flow chart? %
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18.
\begin{figure}[!ht]
\includegraphics[width=4.25in]{../Pictures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\clearpage

@@
